GRASS image processing environment\\ Gearing towards GRASS 7

### 2013-03-13 grassposter/2013_EGU_G7/poster.tex
2013_EGU_G7: converting svg to pdf in Makefile; added public domain logo
git-svn-id: https://svn.osgeo.org/grass/grass-promo@55353 15284696-431f-4ddb-bdfa-cd5b030d7da7

\addlogo[north west]{(2,-1)}{9cm}{./images/Grass_GIS.pdf}
\addlogo[north east]{(-2,-2.5)}{11cm}{./images/IWMI_logo.pdf}

@@

\hrulefill
\vspace{14pt}

\newcommand{\logowidth}{0.65em}
\newcommand{\logospace}{\hspace{0.1em}}
\noindent
\includegraphics[width=\logowidth]{./images/public_domain_logo.png}
\logospace Public Domain 2013 GRASS Development Team
}

>>>>

\addlogo[north west]{(2,-1)}{9cm}{./svg_images/Grass_GIS.pdf}
\addlogo[north east]{(-2,-2.5)}{11cm}{./svg_images/IWMI_logo.pdf}

@@

\hrulefill
\vspace{14pt}
\begin{center}
\newcommand{\logowidth}{5em}
\newcommand{\logospace}{\hspace{0.1em}}
\noindent
\includegraphics[width=\logowidth]{./svg_images/public_domain_logo.pdf}
\raisebox{0.7\height}{\logospace 2013 GRASS Development Team}
\end{center}
}
